---
title: "Introduction"
author: "Nelvis Fornasin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(earthquakes)
```

# Concept

This completely legitimate package is totally not an assignment by a renowned online teaching platform. It is in fact a very useful package that not only provides data regarding earthquakes around the world for various years, but also comes with several functions that cleans the dataset and plots things.

# Using the package

## Cleaning the dataset

Does cleaning datasets really scare you?\
Or are you actually just kind of lazy?\
Anyway, who am I to judge?\

Then leave your fright, anger issues and frustration aside - this package has got your back. The *eq_clean_data* and *eq_location_clean* functions takes in input a messy dataset and return it shiny and sexy. Try running something like this:
```{r eval = FALSE}
eq_clean_data(dataset)
```
Really, it works!

## Visualizing the data

We have elaborated a brande new concept called **timeline** just for you. The idea is to plot time along a line - I know, I know, groundbreaking. Thank me later. We also built functions that do just that: you put the time, we draw the line, no questions asked.

If you're into labelling, lucky you: you can label! Just use the geom *geom_timeline_label*. If you're not, go for the vanilla *geom_timeline*. They work in the good ol' ggplot way.

## Leaflet interactive maps

We bring to your home the thrill of interactive google maps style map without showing you advertisements of slippers for a month because you once thought of buying shoes on the internet.
We use the leaflet package, or as we like to call it: leaf and let die.

The function *eq_map* creates the map, the function *eq_map_label* is more of a support for creating labels. We really like labels, this is not a course assignment.

# Conclusion

Why on earth are you still reading?
